Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-08 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:08	16:47:18	(Tue 8.Sep)
la2pdf commit - 2015:09:08	17:46:31	(Tue 8.Sep)

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, with the same parameters. The location of the anchor and cut line is marked in red. Note how LCA prefers a rectangular window ($\beta=0$) on the anchor.}\label{oversampling_mosaic_bounds_beta}
\end{figure*}

% \setcounter{dbltopnumber}{1}

>>>>

\begin{figure*}[t]\centering
\subfloat[$\beta$-values of the Kaiser window chosen for each image pixel.  Note how LCA prefers a rectangular window ($\beta=0$) on the anchor.]{\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%%
\label{oversampling_mosaic_bounds_beta}}
\hfil
\subfloat[$\beta$-values of the Kaiser window chosen for each image pixel. ]{\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_phi.pdf}%
\label{oversampling_mosaic_bounds_phi}}
\caption{Kaiser windows chosen for each pixel in the image. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, with the same parameters. The location of the anchor, cut line and main scatter locations of the cross is marked in red.}
\label{fig_sim}
\end{figure*}

% \begin{figure*}[t]%\centering%
% \includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
% \caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, with the same parameters. The location of the anchor and cut line is marked in red. Note how LCA prefers a rectangular window ($\beta=0$) on the anchor.}\label{oversampling_mosaic_bounds_beta}
% \end{figure*} 
% 
% \begin{figure*}[t]%\centering%
% \includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_phi.pdf}%
% \caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, with the same parameters. The location of the anchor and cut line is marked in red. Note how LCA prefers a rectangular window ($\beta=0$) on the anchor.}\label{oversampling_mosaic_bounds_beta}
% \end{figure*}

% % \setcounter{dbltopnumber}{1}
